---
title: "my_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Introduction
This vingette will guide you how the `linreg` package works with the help of the IRIS dataset that is already in RStudio.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Create a model
```{r}
model <- linreg$new(formula=Petal.Length~Sepal.Width+Sepal.Length, data=iris)
```

## The plot() function in the linreg-package
With the plot function the package will create one Residuals VS Fitted Values graph and one Scale-Locaion graph from the formula you just have created.

```{r plot}

model$plot()
```


## The resid() function in the linreg-package
With the resid function the package will return a vector with the models residuals
```{r plot}

model$resid()
```


## The pred() function in the linreg-package
With the pred function the package will return the predicted values for the model
```{r plot}

model$pred()
```


## The coef() function in the linreg-package
With the coef function the package will return the named coefficients for the model 
```{r plot}

model$coef()
```


## The summary() function in the linreg-
With the summary function the package will print out a summary with the models coefficients, standard errors, t-values, p-values, estimations of $\hat{\sigma}$ and the degrees of freedoms.
```{r plot}

model$summary()
```


## The plot() function in the linreg-package
With the plot function the package will create
```{r plot}

model$summary()
```



