---
title: "Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction  
This vingette will guide you how the `linreg` package works with the help of the IRIS dataset that is already in RStudio.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
data("iris")
library(lab4)
```

## Dataset used to guide how the package works
We will use the Iris dataset here to show how the package work. The dataset contains 5 variables, Sepal.Length, Sepal.Width, Petal.Length, Petal.Width and Species. The first 4 are continuous measured and the species variable is a factor with the 3 flower Species (setosa, versicolor, virginica). The dataset contains of total 150 observations. 
```{r}
data(iris)
head(iris)
```


## Create a model
Here we build a linear regression, in the formula you set the dependent variable on the left side of the $\sim$ sign and the independent variables on the right side of the sign. In data you include the dataframe where the variables are.  
```{r}
model <- linreg$new(formula=Petal.Length~Sepal.Width+Sepal.Length, data=iris)
```

## The plot() function in the linreg-package
With the plot function the package will create one Residuals VS Fitted Values graph and one Scale-Locaion graph from the formula you just have created.

```{r fig.height=5, fig.width=5, message=FALSE, warning=FALSE}

model$plot()
```


## The resid() function in the linreg-package
With the resid function the package will return a vector with the models residuals $\hat{e_i}$
```{r resid}

head(model$resid())
```


## The pred() function in the linreg-package
With the pred function the package will return the predicted values $\hat{y_i}$ for the model
```{r pred}

head(model$pred())
```


## The coef() function in the linreg-package
With the coef function the package will return the named coefficients $\hat{\beta_i}$for the model 
```{r coef}

model$coef()
```


## The summary() function in the linreg-
With the summary function the package will print out a summary with the models coefficients, standard errors, t-values, p-values, estimations of $\hat{\sigma}$ and the degrees of freedoms.
```{r summary}

model$summary()
```





